\tool

### 2018-04-04 paper/paper.tex

\begin{abstract}
To increase software user productivity, toolsmiths create tools and features to automatically complete software tasks. However, these useful tools are often undiscovered or ignored by potential users, which can be problematic for industries, such as software engineering, that rely on worker efficiency and correctness. This paper introduces \tool, a novel automated recommendation system developed for researchers to make recommendations and increase awareness of their products. To help improve tool adoption among software engineers, \tool~integrates concepts from peer interactions and software engineering industry practices to suggest tools to developers, and our results suggest that this approach is effective in making tool recommendations to software developers on GitHub repositories.
\end{abstract}
\keywords{Software Engineering; Tool Recommendations; Tool Discovery;}

@@

Software is becoming increasingly prevalent in our society. To keep up with rising demands for new technology, software engineers are making efforts to emphasize \textit{software quality}. Throughout the software development life cycle, companies focus on metrics that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}. However, despite increased attention to improving software quality, buggy code remains a persisting and escalating problem.

The 2017 Software Fail Watch by Tricentis discovered that software failures affected approximaltely half of the world's population impacting 3.7 billion users, and caused \$1.7 trillion in financial losses.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs in code, or debugging, continues to become increasingly time-consuming and costly.  A study by the National Institute of Standards and Technology reported that software engineers spend 70-80\% of their time debugging at work, and one error takes an average of 17.4 hours to debug~\cite{NIST}. Studies also show the cost of fixing an error becomes more expensive the longer it exists in source code~\cite{SEEconomics, SoftwareAssuranceSDLC}.

To improve code quality and prevent errors, researchers and toolsmiths have created software engineering tools to aid developers in their work. Prior work shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, and more are beneficial for improving code. These tools automatically perform a wide variety of software development tasks to save time and effort for developers. Additionally, the Software Engineering Body of Knowledge indicates the importance of development tools, noting they can be used to achieve ``desirable characteristics of software products''~\cite{SWEBOK}. Utilizing software enginering tools can reduce software errors and debugging costs while increasing developer productivity.

Althouth quality is a primary concern for developers and users and many software engineering tools exist to help improve code and prevent bugs, developers rarely use these tools~\cite{Johnson2013Why}. One of the primary barriers to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness for software engineering tools can lead to poor code quality, inconvenienced users, and significant amounts of time and money spent fixing errors. While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interaction}, is the most effective mode of tool discovery~\cite{MurphyHill2011PeerInteraction}.

To help solve the tool discovery problem among software engineers, we developed \tool. Our system automatically recommends development tools by analyzing developer changes and integrating characteristics of peer interactions and software engineering practices. \tool~is designed for toolsmiths to increase awareness of their products by systematically running their tools and making customized recommendations to developers on GitHub\footnote{https://github.com}, the largest code hosting platform in the world~\cite{GousiosGitHub}. This paper seeks to answer the following research questions (RQs): \\

\noindent
\textbf{RQ1:} How applicable is \tool~to real-world software applications?  \\ 
\textbf{RQ2:} How useful are recommendations from \tool~to developers?  \\

To answer these questions, we evaluated \tool~recommending \textsc{Error Prone}\footnote{http://errorprone.info}, an open source Java static analysis tool. We examined the frequency of recommendations and how developers reacted to receiving suggestions from our system. This research makes the following contributions:

\begin{itemize}
 \item a novel recommender system for researchers to increase awareness of their software engineering tools, and
 \item an evaluation of \tool~ recommending \textsc{Error Prone} to GitHub developers
 \end{itemize}

\section{Related Work}
%TODO: Use related work from whatever conference committee
Our implementation of \tool~builds on previous research examining tool discovery, lack of tool adoption among software engineers, and automated recommendation systems.

Researchers have explored how humans learn about new tools. There are various methods to discover tools in software, and research suggests recommendations between peers is the most effective way to increase tool awareness. Murphy-Hill found that peer interactions were the most effective mode of tool discovery compared to tool encounters, tutorials, descriptions, social media, and discussion threads~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}. Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}. To improve the effectiveness of recommendations from our system, we integrate qualities of peer interactions into \tool.

@@

\section{Tool}
\tool~aims to increase discovery and adoption of useful software engineering tools among developers. This section describes the design and implementation of our approach.

\subsection{Peer Interactions}
Previous research shows that recommendations between colleagues is the most effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}. Murphy-Hill interviewed software engineers and found that user-to-user peer interactions occur less frequently but are much more effective that system-to-user solutions.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.

@@

The primary desire of software users is to have enjoyable and problem-free experiences with software. Developers of these applications also have similar desires, to create high-quality and functioning programs for users. A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}. To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help accomplish these tasks. However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}. \tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.

@@

@@

\subsubsection{Fix Identification}

@@

%\pseudosubsection{Fix Localizaton}
%TODO: Delete?
%When a fix is identified in the changed version of code, \tool~then aims to find the location of the fix in the head version. To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees. We look for the action closest to the offset of the error node calculated from the bug line number reported by the software engineering tool, if applicable. If the closest action is not a delete, then our approach take the location takes the location of that action. Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent. Additionally, the line of the fix had to be converted to the equivalent position in the pull request or commit diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.

@@

To get the most popular repositories, we filtered GitHub projects by the amount of stars based on numbers in the Fibonnaci sequence. We chose the most starred repositories to study the most popular projects on GitHub. Stars are a social aspect of GitHub where users can indicate their favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}. Using Fibonacci numbers allowed us to get a higher concentration of projects with a lower amount of stars, while fewer projects will have a very large number of stars. To filter of repositories, we grouped projects with 1 or 2 stars, 2 or 3 stars, between 3 and 5 stars, between 5 and 8 stars, etc., and sorted the top 100 projects in each group by when they were most recently updated. After using a GitHub search API to find projects that met the above criteria, we compiled a list of 789 code repositories. The projects used for our evaluation include a wide range of software applications providing a variety of services from large software companies such as Google and Apache to individual developers. A list of projects used for this study is publicly available online.\footnote{\url{https://gist.github.com/tool-recommender-bot/1769ccd148508beabcd273a731723860}}
%TODO: Maybe examples of projects?

>>>>

\begin{abstract}
To increase software engineer productivity, toolsmiths create tools and features to automatically complete software development tasks. However, these useful tools are often undiscovered or ignored by developers which is problematic for software applications that rely on programmer efficiency and correctness. This paper introduces \tool, an automated recommendation system created for researchers to increase awareness of their products by making recommendations to developers on online collaboration websites. To help improve tool adoption among software engineers, \tool~uses a novel approach and original design principles to integrate concepts of user-to-user suggestions and industry practices in tool recommendations to developers, and our results suggest this approach is more effective in making tool recommendations to software developers on GitHub repositories.
\end{abstract}
\keywords{Tool Recommendations; Tool Discovery;}

@@

To keep up with rising demands for technology, software engineers emphasize \textit{software quality}. Throughout the software development life cycle, development teams monitor code metrics that impact expectations of software producers and consumers~\cite{KitchenhamQualityTarget}. However, despite increased attention to software quality, buggy code remains a problem. The Software Fail Watch by Tricentis suggests software failures impacted 3.7 billion users and caused \$1.7 trillion in financial losses in 2017.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs, or debugging, is a time-consuming and costly activity. The National Institute of Standards and Technology reports software engineers spend 70-80\% of work time debugging and the average time to debug one error is 17.4 hours~\cite{NIST}. Fixing defects early in the development process is also important since studies show debugging costs increase the longer a bug remains in code~\cite{SEEconomics, SoftwareAssuranceSDLC}.

To improve code quality and prevent errors, researchers and toolsmiths have created software engineering tools to aid developers in their work. Prior work shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, and more are beneficial for improving code and preventing bugs. These tools can automatically perform a wide variety of software development tasks to save time and effort for developers. Additionally, the Software Engineering Body of Knowledge recommends using development tools because they can be used to achieve ``desirable characteristics of software products''~\cite{SWEBOK}. Utilizing software enginering tools can reduce software errors and debugging costs while increasing developer productivity.

Although quality is a concern for developers and users, many helpful software engineering tools go unused by developers. One of the primary barriers to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness for software engineering tools can lead to poor code quality, inconvenienced users, and significant amounts of time and money spent fixing errors. While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interaction}, compared to other modes of tool discovery~\cite{MurphyHill2011PeerInteraction}. Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.

To help solve the tool discovery problem among software engineers, we developed \tool. Our system automatically recommends development tools by analyzing developer changes and integrating characteristics of peer interactions and software engineering practices. \tool~is designed for toolsmiths to increase awareness of their products by systematically running their tools and making customized recommendations to developers, the largest code hosting platform in the world~\cite{GousiosGitHub}. This paper presents the novel approach and design of our system and evaluates the effectiveness of our tool in a real-world scenario.

%\noindent
%TODO: Research questions?
%\textbf{RQ1:} How applicable is \tool~to real-world software applications?  \\ 
%\textbf{RQ2:} How useful are recommendations from \tool~to developers?  \\

To evaluate \tool, we conducted a study making recommendations for \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool, to developers on the GitHub\footnote{https://github.com} code hosting platform. We calculated the effectiveness of \tool~by measuring the frequency of recommendations and how developers reacted to receiving suggestions from our system. This research makes the following contributions:

\begin{itemize}
 \item a novel approach for recommender systems to increase awareness of software engineering tools, and
 \item an evaluation of \tool~ recommending \textsc{Error Prone} to developers on GitHub.
 \end{itemize}

\section{Related Work}
%TODO: Use related work from whatever conference committee
Our implementation of \tool~builds on previous research examining recommendation systems in software engineering, techniques for learning new tools and features, approaches for tool recommendations, and existing systems that recommend software engineering tools.

@@

\section{Approach}

\tool~aims to increase discovery and adoption of useful software engineering tools by implementing three design pillars: \textit{commend}, \textit{apprehend}, and \textit{recommend}.

\subsection{Commend}

\subsection{Apprehend}

\subsection{Recommend}

\section{Design}

Previous research peer interactions influenced our three design pillars for \tool.

\subsection{Peer Interactions}
Previous research shows that recommendations between colleagues are the most effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}. Murphy-Hill interviewed software engineers and found that user-to-user peer interactions occur less frequently in the workplace but are more effective than system-to-user solutions.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.

@@

A key desire of software users is to have enjoyable and problem-free experiences with software. Producers of software applications also have a similar desire to create high-quality functioning programs for users. A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}. To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help accomplish these tasks. However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}. \tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.

@@

\section{Implementation Walkthrough}

\section{Implementation Description}

@@

\subsubsection{Debugging}

@@

When a fix is identified in the changed version of code, \tool~then aims to find the location of the fix in the head version. To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees. We look for the action closest to the offset of the error node calculated from the bug line number reported by the software engineering tool, if applicable. If the closest action is not a delete, then our approach take the location takes the location of that action. Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent. Additionally, the line of the fix had to be converted to the equivalent position in the pull request or commit diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.

@@

To get the most popular repositories, we filtered GitHub projects by the amount of stars based on numbers in the Fibonnaci sequence. We chose the most starred repositories to study the most popular projects on GitHub. Stars are a social aspect of GitHub where users can indicate their favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}. Using Fibonacci numbers allowed us to get a higher concentration of projects with a lower amount of stars, while fewer projects will have a very large number of stars. To filter of repositories, we grouped projects with 1 or 2 stars, 2 or 3 stars, between 3 and 5 stars, between 5 and 8 stars, etc., and sorted the top 100 projects in each group by when they were most recently updated. After using a GitHub search API to find projects that met the above criteria, we compiled a list of 789 code repositories. Out of those projects, one repository failed due to broken Unicode text. %TODO: find other failed projects w/ errors
The projects used for our evaluation include a wide range of software applications providing a variety of services from large software companies such as Google and Apache to individual developers. A list of projects used for this study is publicly available online.\footnote{\url{https://gist.github.com/tool-recommender-bot/1769ccd148508beabcd273a731723860}}
%TODO: Maybe examples of projects?
